A new metric for automatic discovery of periodic patterns in time series

### 2021-03-03 paper/main.Rmd
abstract added

- name: Dianne Cook
  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia

bibliography: bibliography.bib
preamble: >
  \usepackage{mathtools,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \usepackage{algorithm}
  \usepackage{algorithmicx}
  \usepackage{algpseudocode}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    #base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
---

>>>>

- name: Dianne Cook
  affiliation: Department of Econometrics and Business Statistics, Monash University, Australia
keywords:
- data visualization
- periodicities
- time granularities
- cyclic granularities
- permutation tests
- Jensen-Shannon distances
- smart meter data
- R

abstract: |
 Periodic patterns or associations in large univariate time series data could be discerned by analysing the behaviour across cyclic temporal granularities, which are temporal deconstructions accounting for repetitive behaviour. The temporal granularities form ordered categorical variables and display of distributions of the univariate response variable across two or more combinations of these categorical variable can help explore periodicities, patterns and anomalies. A  pair of granularities that can be meaningfully examined together are called “harmonies” and the ones which cannot be are called “clashes”. Even after excluding clashes, the list of harmonies that could potentially be displayed is huge and hence overwhelming for human consumption. This work provides a methodology to screen the most informative graphics from the plethora of choices by introducing a distance measure that could be compared across harmonies with varied levels and data sets. Moreover, this distance measure could also be used to rank the selected harmonies basis how well they capture the variation in the measured variable. All the methods are implemented in the open source R package `hakear`.

bibliography: [bibliography.bib]
preamble: >
  \usepackage{mathtools,amssymb,booktabs,amsthm,todonotes,colortbl}
  \def\mod{~\text{mod}~}
  \newtheorem{definition}{Definition}
  \usepackage{mathptmx}
  \usepackage{caption}
  \DeclareCaptionStyle{italic}{labelfont={bf},textfont={it},labelsep=colon}
  \captionsetup[figure]{style=italic,format=hang,singlelinecheck=true}
  \captionsetup[table]{style=italic,format=hang,singlelinecheck=true}
  \def\novspacing{\setlength{\aboverulesep}{0pt}\setlength{\belowrulesep}{0pt}}
  \def\vspacing{\setlength{\aboverulesep}{0.4ex}\setlength{\belowrulesep}{0.65ex}}
output:
  bookdown::pdf_book:
    base_format: rticles::asa_article
    fig_height: 5
    fig_width: 8
    fig_caption: yes
    dev: "pdf"
    keep_tex: yes
---
